MSTK: Mesh Toolkit, v 1.3 - DRAFT

### 2004-07-09 docs/MSTK.tex
Updated docs to reflect new functions

\title{MSTK: Mesh Toolkit, v 1.2 - DRAFT}

@@

\par MSTK will soon allow applications to attach application or field data
to entities. This data may be integers, reals (doubles), integer
vectors, real (double) vectors, integer tensors, real (double tensors)
and pointers.

@@

\begin{description}
\item[]\textbf{\textit{List\_ptr}}: Handle to a List object

@@

\item[]\textbf{\textit{MVertex\_ptr}}: Handle to a Mesh Vertex object (Topological
Dimension 0)

\item[]\textbf{\textit{MEdge\_ptr}}: Handle to a Mesh Edge object (Topological Dimension 1)

\item[]\textbf{\textit{MFace\_ptr}}: Handle to a Mesh Face object (Topological Dimension 2)

\item[]\textbf{\textit{MRegion\_ptr}}: Handle to Mesh Region object (Topological Dimension 3)

\item[]\textbf{\textit{MEntity\_ptr}}: Handle to a generic Mesh Entity object. Any of
the above types of entities can be cast as \textit{MEntity\_ptr}

\item[]\textbf{\textit{GModel\_ptr}}: Handle to a Geometric Model object
\item[]\textbf{\textit{GEntity\_ptr}}: Handle to a Geometric Entity object

\item[]\textbf{\textit{RepType}}: Enumerated type describing the type
  of mesh representation.  Can be UNKNOWN\_REP, F1, F4, R1, R2, R4.
  See Appendix~\ref{app:reptypes} for schematics of these
  representations \textit{Currently only representation types F1 and
    F4 are supported}

\item[]\textbf{\textit{MFType}}: Enumerated type for mesh face type
Can be FDELETED, FUNKNOWN, TRI, QUAD, POLYGON

\item[]\textbf{\textit{MRType}}: Enumerated type for mesh region type
Can be RDELETED, RUNKNOWN, TET, PYRAMID, PRISM, HEX, POLYHED
\end{description}

@@

The value of the iteration index i will be modified by the routine on
each call to indicate where in the set it is. This value should not be
modified externally while iterating through the set. Also, no specific
meaning be derived from from the iteration index by other applications
since the internal implementation and interpretation of the index may
change at any time.

@@

@@

@@

@@

\item[]\textbf{\textit{void} MESH\_Add\_Vertex(\textit{Mesh\_ptr} mesh,
\textit{MVertex\_ptr} v):} Add a vertex to the mesh. It is assumed that
the vertex and its coordinates set are properly defined.

\item[]\textbf{\textit{void} MESH\_Add\_Edge(\textit{Mesh\_ptr} mesh,
\textit{MEdge\_ptr} e):} Add an edge to the mesh. It is assumed that
the edge is and its topology is defined.

\item[]\textbf{\textit{void} MESH\_Add\_Face(\textit{Mesh\_ptr} mesh,
\textit{MFace\_ptr} f):} Add a face to the mesh. It is assumed that the
face and its topology is properly defined.

\item[]\textbf{\textit{void} MESH\_Add\_Region(\textit{Mesh\_ptr} mesh,
\textit{MRegion\_ptr} r):} Add a region to the mesh. It is assumed that
the region and its topology is properly defined.

\item[]\textbf{\textit{void} MESH\_Rem\_Vertex(\textit{Mesh\_ptr} mesh,
\textit{MVertex\_ptr} v):} Remove vertex from mesh. Vertex is not
deleted and must be deleted afterward separately.

\item[]\textbf{\textit{void} MESH\_Rem\_Edge(\textit{Mesh\_ptr} mesh,
\textit{MEdge\_ptr} e):} Remove edge from mesh. Edge is not deleted and
must be deleted afterward separately.

\item[]\textbf{\textit{void} MESH\_Rem\_Face(\textit{Mesh\_ptr} mesh,
\textit{MFace\_ptr} f):} Remove face from mesh. Face is not deleted and
must be deleted afterward separately.

\item[]\textbf{\textit{void} MESH\_Rem\_Region(\textit{Mesh\_ptr} mesh,
\textit{MRegion\_ptr} r):} Remove region from mesh. Region is not deleted and must be deleted afterward separately.

@@

@@

\item[]\textbf{\textit{void} MV\_Delete(\textit{MVertex\_ptr} mvertex):}
Delete the vertex. Deletes all topological and geometric
information embedded in the vertex.

@@

\item[]\textbf{\textit{void} MV\_Set\_GEntity(\textit{MVertex\_ptr} mvertex,
GEntity\_ptr gent):} Set the geometric model entity on which vertex is
classified.

@@

\item[]\textbf{\textit{void} ME\_Delete(\textit{MEdge\_ptr} medge):} Delete
the edge. Deletes all topological information embedded in the edge.

@@

\item[]\textbf{\textit{void} MF\_Delete(\textit{MFace\_ptr} mface):} Delete
the face. Delete all topological information embedded in the face.

\item[]\textbf{\textit{void} MF\_Set\_GEntity(\textit{MFace\_ptr} mface, GEntity\_ptr gent):} Set the geometric model entity on which the edge is classified.

@@

\item[]\textbf{\textit{void} MF\_Set\_ID(\textit{MFace\_ptr} mface,
\textit{int} id):} Explicitly set ID of an edge and overwrite the ID
set by the MF\_New operator. Does not check for duplication of face
IDs.

@@

\item[]\textbf{\textit{void} MF\_Set\_Vertices(\textit{MFace\_ptr} mface,
\textit{int} n, \textit{MVertex\_ptr} *verts):} Set the vertices of the
face. The ordered set of vertices is passed in through an array along
with the number of vertices. The vertices are assumed to be ordered
clockwise around the face. This function is relevant only for reduced
representations in MSTK.

\item[]\textbf{\textit{void} MF\_Replace\_Edge(\textit{MFace\_ptr} mface,
\textit{MEdge\_ptr} edge, \textit{MEdge\_ptr} nuedge, \textit{int}
dir):} Replace an edge in the face with another edge. The direction
in which the new edge is used in the face must also be supplied. This
function is relevant only for full representations in MSTK.

@@

\item[]\textbf{\textit{void} MF\_Replace\_Edge\_i(\textit{MFace\_ptr} mface,
\textit{int} i, \textit{MEdge\_ptr} nuedge, \textit{int} dir):} Replace
the i'th edge in the face with another edge. The direction in which the
new edge is used in the face must also be supplied. This function is
relevant only for full representations in MSTK.

@@

@@

@@

\item[]\textbf{\textit{void} MR\_Delete(\textit{MRegion\_ptr} mregion):}
Delete the region. Deletes all topological information embedded in the
edge.

\item[]\textbf{\textit{void} MR\_Set\_GEntity(\textit{MRegion\_ptr} mregion,
GEntity\_ptr gent):} Set the geometric model entity on which the edge
is classified.

\item[]\textbf{\textit{void} MR\_Set\_GEntDim(\textit{MRegion\_ptr} mregion,
\textit{int} gdim):} Set the dimension of the geometric model entity on
which the edge is classified.

\item[]\textbf{\textit{void} MR\_Set\_GEntID(\textit{MRegion\_ptr} mregion,
\textit{int} gid):} Set the ID of the geometric model entity on which
the edge is classified.

\item[]\textbf{\textit{void} MR\_Set\_ID(\textit{MRegion\_ptr} mregion,
\textit{int} id):} Explicitly set ID of an edge and overwrite the ID
set by the \textbf{MR\_New} function. Does not check for duplication
of region IDs.

@@

\item[]\textbf{\textit{void} MR\_Set\_Vertices(\textit{MRegion\_ptr}
mregion, \textit{int} nv, \textit{MVertex\_ptr} *mvertices):} Set the
vertices of the region. This function is relevant for reduced
representations only. For standard elements, the vertices must be
ordered as indicated in Appendix~\ref{app:reg_conventions}. This
function does not apply for defining general regions since there
cannot be any implicit ordering.

\item[]\textbf{\textit{void} MR\_Replace\_Face(\textit{MRegion\_ptr}
mregion, \textit{MFace\_ptr} mface, \textit{MFace\_ptr} nuface,
\textit{int} dir):} Replace a face of the region with another edge. The
direction in which the new face is used in the region must also be
supplied. This function is only relevant for full representations in
MSTK.

@@

@@

\item[]\textbf{\textit{GEntity\_ptr} MEnt\_GEntity(\textit{MEntity\_ptr} mentity):}
Returns a pointer or handle to geometric model entity that the entity
is classified on.
\end{description}

>>>>

\title{MSTK: Mesh Toolkit, v 1.3 - DRAFT}

@@

\par To support numerical analysis and other applications, MSTK allows
applications to attach application or field data to entities. This
data may be integers, reals (doubles), integer vectors, real (double)
vectors, integer tensors, real (double tensors) and pointers.

@@

\begin{description}
\item[]\textbf{\textit{List\_ptr}}: Handle to a List object.

@@

\item[]\textbf{\textit{MVertex\_ptr}}: Handle to a Mesh Vertex object (Topological
Dimension 0).

\item[]\textbf{\textit{MEdge\_ptr}}: Handle to a Mesh Edge object (Topological Dimension 1).

\item[]\textbf{\textit{MFace\_ptr}}: Handle to a Mesh Face object (Topological Dimension 2).

\item[]\textbf{\textit{MRegion\_ptr}}: Handle to Mesh Region object (Topological Dimension 3).

\item[]\textbf{\textit{MEntity\_ptr}}: Handle to a generic Mesh Entity
  object. Any of the above types of entities can be cast as
  \textit{MEntity\_ptr}.

\item[]\textbf{\textit{GModel\_ptr}}: Handle to a Geometric Model object.
\item[]\textbf{\textit{GEntity\_ptr}}: Handle to a Geometric Entity object.

\item[]\textbf{\textit{MAttrib\_ptr}}: Handle to a mesh attribute.

\item[]\textbf{\textit{RepType}}: Enumerated type describing the type
  of mesh representation.  Can be UNKNOWN\_REP, F1, F4, R1, R2, R4.
  See Appendix~\ref{app:reptypes} for schematics of these
  representations. \textit{Currently only representation types F1 and
    F4 are supported}.

\item[]\textbf{\textit{MType}}: Enumerated type for mesh entity type. Can be MDELETED, MVERTEX, MEDGE, MFACE, MREGION, MUNKNOWNTYPE, MALLTYPE.

\item[]\textbf{\textit{MFType}}: Enumerated type for mesh face type.
Can be FDELETED, FUNKNOWN, TRI, QUAD, POLYGON.

\item[]\textbf{\textit{MRType}}: Enumerated type for mesh region type.
Can be RDELETED, RUNKNOWN, TET, PYRAMID, PRISM, HEX, POLYHED.

\item[]\textbf{\textit{AttType}}: Enumerated type for attribute data. Can be INT, DOUBLE or POINTER
\end{description}

@@

The value of the iteration index i will be modified by the routine on
each call to indicate where in the set it is. This value should not be
modified externally while iterating through the set. Also, no specific
meaning should be derived from the iteration index by other applications
since the internal implementation and interpretation of the index may
change at any time.

@@

\item[]\textbf{\textit{int} MESH\_ImportFromFile(\textit{Mesh\_ptr}
    mesh, const char *filename, const char *format):} Import a mesh
  data from an external file format and construct MSTK mesh. Currently
  the only format supported is the
  GMV\footnote{\texttt{http://www-xdiv.lanl.gov/XCM/gmv/GMVHome.html}}
  file format. The routine imports as many attributes as it can from
  the input file. It also uses special attributes or keywords as data
  about element and node classification.  For GMV files, the routine
  uses the ``material'' data to indicate region or face classification
  depending on the dimensionality of the mesh. If ``material'' data is
  not specified, it uses the ``itetclr'' attribute to assign region or
  face classification. It also uses the ``icr'' keyword describing the
  number of constraints on a node to interpret if the node is
  classified on a model region, model face, model edge or a model
  vertex. The ``itetclr'' and ``icr'' keywords are usually present in
  meshes generated by
  LAGRIT\footnote{\texttt{http://lagrit.lanl.gov'}}.

\item[]\textbf{\textit{int} MESH\_BuildClassfn(\textit{Mesh\_ptr}
    mesh):} Build classification information for mesh entities if only
  partial information is present. In other words, if the only data
  known is the IDs of geometric model entities (``material regions'')
  of the highest level mesh entities (faces or regions), then this
  procedure will build information about the type of geometric model
  entities that the lower dimension entities are on. Faces will be
  classified as being on a model face (external or interior) or inside
  model region. Edges will be classified as being on a model edge,
  model face or in a model region. Vertices will be classified as
  being on a model vertex, model edge, model face or in a model
  region. If no classification data is associated with even the
  highest level entities, the procedure will assume that all the
  highest level entities are classified on one model entitiy of that
  dimension. If partial information is available for lower order
  entities, this routine will not destroy that information. In the
  future, the procedure will be more sophisticated, incorporating
  features such as classifying mesh edges as being on model edges if
  the dihedral angle between the boundary faces connected to it is
  very large.

@@

%% \item[]\textbf{\textit{void} MESH\_ExportToFile(\textit{Mesh\_ptr}
%%     mesh, const char *filname, const char *format, int natt, char
%%     **attnames):} Export a mesh to an external file format. Currently,
%%   the formats supported are the GMV file (format string: ``gmv'') and
%%   Data Explorer\footnote{\texttt{http://opendx.org}} (format string:
%%   ``dx''). Only integer and double attributes of the mesh are exported
%%   to the files.

\item[]\textbf{\textit{void} MESH\_ExportToFile(\textit{Mesh\_ptr}
    mesh, const char *filname, const char *format, int natt, char
    **attnames):} Export a mesh to an external file format. Currently,
  the only format supported is the GMV file format (format string:
  ``gmv''). Only integer and double attributes of the mesh are
  exported to the files.

\item[]

@@

\item[]

@@

\item[]\textbf{\textit{MRegion\_ptr}
    MESH\_Next\_Region(\textit{Mesh\_ptr} mesh, \textit{int} *idx):}
  Returns the next region while iterating through the regions of the
  mesh. See the routine \textbf{List\_Next\_Entry} above for an
  explanation of how the iteration works.

\item[]

\item[]\textbf{\textit{MVertex\_ptr}
    MESH\_VertexFromID(\textit{Mesh\_ptr} mesh, \textit{int} id):}
  Return mesh vertex with given ID if it exists; return NULL
  otherwise.

\item[]\textbf{\textit{MEdge\_ptr} MESH\_EdgeFromID(\textit{Mesh\_ptr}
    mesh, \textit{int} id):} Return mesh edge with given ID if it
  exists; return NULL otherwise. This routine will return NULL for all
  reduced representations.

\item[]\textbf{\textit{MFace\_ptr} MESH\_FaceFromID(\textit{Mesh\_ptr}
    mesh, \textit{int} i):} Return mesh face with given ID if it
  exists; return NULL otherwise. If faces are not explicitly
  represented in the mesh, it will return NULL.

\item[]\textbf{\textit{MRegion\_ptr}
    MESH\_RegionFromID(\textit{Mesh\_ptr} mesh, \textit{int} id):}
  Return mesh region with given ID if it exists; return NULL
  otherwise.

\item[]

\item[]\textbf{\textit{int} MESH\_Num\_Attribs(\textit{Mesh\_ptr}
    mesh):} Number of attributes associated with the mesh.

\item[]\textbf{\textit{MAttrib\_ptr} MESH\_Attrib(\textit{Mesh\_ptr}
    mesh, \textit{int} i):} Return the i'th attribute in the mesh.
  Returns NULL if i $<$ 0 or i $>$ number of mesh attributes.

\item[]\textbf{\textit{MAttrib\_ptr}
    MESH\_Next\_Attrib(\textit{Mesh\_ptr} mesh, \textit{int} *index):}
  Returns the next attribute while iterating through the attributes of
  the mesh. See the routine List\_Next\_Entry above for an explanation
  of how the iteration works.

\item[]\textbf{\textit{MAttrib\_ptr}
    MESH\_AttribByName(\textit{Mesh\_ptr} mesh, \textit{const char}
    *name):} Return a mesh attribute with given name if it exisists in
  the mesh. Returns NULL if mesh has no such attribute.

\item[]

@@

\item[]

\item[]\textbf{\textit{void} MESH\_Add\_Vertex(\textit{Mesh\_ptr}
    mesh, \textit{MVertex\_ptr} v):} Add a vertex to the mesh. It is
  assumed that the vertex and its coordinates set are properly
  defined. Normally, one need not call this since
  \textbf{\textit{MV\_New}} will add the vertex to the mesh. Use this
  only if you know exactly what you are doing.

\item[]\textbf{\textit{void} MESH\_Add\_Edge(\textit{Mesh\_ptr} mesh,
    \textit{MEdge\_ptr} e):} Add an edge to the mesh. It is assumed
  that the edge is and its topology is defined. Normally, one need not
  call this since \textbf{\textit{ME\_New}} will add the edge to the
  mesh. Use this only if you know exactly what you are doing.

\item[]\textbf{\textit{void} MESH\_Add\_Face(\textit{Mesh\_ptr} mesh,
    \textit{MFace\_ptr} f):} Add a face to the mesh. It is assumed
  that the face and its topology is properly defined. Normally, one
  need not call this since \textbf{\textit{MF\_New}} will add the face
  to the mesh. Use this only if you know exactly what you are doing.

\item[]\textbf{\textit{void} MESH\_Add\_Region(\textit{Mesh\_ptr}
    mesh, \textit{MRegion\_ptr} r):} Add a region to the mesh. It is
  assumed that the region and its topology is properly defined.
  Normally, one need not call this since \textbf{\textit{MR\_New}}
  will add the region to the mesh. Use this only if you know exactly
  what you are doing.

\item[]\textbf{\textit{void} MESH\_Rem\_Vertex(\textit{Mesh\_ptr}
    mesh, \textit{MVertex\_ptr} v):} Remove vertex from mesh. Vertex
  is not deleted and must be deleted afterward separately. Normally,
  one need not call this since \textbf{\textit{MV\_Delete}} will
  remove the vertex from the mesh. Use this only if you know exactly
  what you are doing.

\item[]\textbf{\textit{void} MESH\_Rem\_Edge(\textit{Mesh\_ptr} mesh,
    \textit{MEdge\_ptr} e):} Remove edge from mesh. Edge is not
  deleted and must be deleted afterward separately. Normally, one need
  not call this since \textbf{\textit{ME\_Delete}} will remove the
  edge from the mesh. Use this only if you know exactly what you are
  doing.

\item[]\textbf{\textit{void} MESH\_Rem\_Face(\textit{Mesh\_ptr} mesh,
    \textit{MFace\_ptr} f):} Remove face from mesh. Face is not
  deleted and must be deleted afterward separately. Normally, one need
  not call this since \textbf{\textit{MF\_Delete}} will remove the
  face from the mesh. Use this only if you know exactly what you are
  doing.

\item[]\textbf{\textit{void} MESH\_Rem\_Region(\textit{Mesh\_ptr}
    mesh, \textit{MRegion\_ptr} r):} Remove region from mesh. Region
  is not deleted and must be deleted afterward separately. Normally,
  one need not call this since \textbf{\textit{MR\_Delete}} will
  remove the region from the mesh. Use this only if you know exactly
  what you are doing.
\end{description}

@@

\item[]\textbf{\textit{void} MV\_Delete(\textit{MVertex\_ptr} mvertex,
    \textit{int} keep):} Delete the vertex. If \textbf{keep} is 0, the
  vertex is removed from the mesh and all topological and geometric
  information embedded in the vertex is destroyed. If \textbf{keep} is
  1, the vertex is marked as type \textit{MDELVERTEX} and removed from
  the mesh but the vertex is not destroyed.

\item[]\textbf{\textit{void} MV\_Restore(\textit{MVertex\_ptr}
    mvertex):} Restore a deleted vertex. The vertex type is restored
  from \textit{MDELVERTEX} to \textit{MVERTEX} and the vertex is
  added back to the mesh.

\item[]

@@

\item[]\textbf{\textit{void} V\_Set\_GEntity(\textit{MVertex\_ptr}
    mvertex, GEntity\_ptr gent):} Set the geometric model entity on
  which vertex is classified.

@@

\item[]\textbf{\textit{void} ME\_Delete(\textit{MEdge\_ptr} medge,
    \textit{int} keep):} Delete the edge. If \textbf{keep} is 0, the
  edge is removed from the mesh and all topological and geometric
  information embedded in the edge is destroyed. If \textbf{keep} is
  1, the edge is marked as type \textit{MDELEDGE} and removed from the
  mesh but the edge is not destroyed. Also, the vertices of this edge
  no longer point to this edge.

\item[]\textbf{\textit{void} ME\_Restore(\textit{MEdge\_ptr}
    medge):} Restore a temporarily deleted edge. The edge type is
  restored from \textit{MDELEDGE} to \textit{MEDGE} and the edge is
  added back to the mesh. The vertices of the edge once again point
  back to the edge.

\item[]

@@

\item[]\textbf{\textit{void} MF\_Delete(\textit{MFace\_ptr} mface):}
  Delete the face. If \textbf{keep} is 0, the face is removed from the
  mesh and all topological and geometric information embedded in the
  face is destroyed. If \textbf{keep} is 1, the face is marked as type
  \textit{MDELFACE} and removed from the mesh but the face is not
  destroyed. Also, the vertices/edges of this face no longer point up
  to this face.

\item[]\textbf{\textit{void} MF\_Restore(\textit{MFace\_ptr}
    mface):} Restore a temporarily deleted face. The face type is
  restored from \textit{MDELFACE} to \textit{MFACE} and the face is
  added back to the mesh. The vertices/edges of the face once again point
  back to the face.

\item[]

\item[]\textbf{\textit{void} MF\_Set\_GEntity(\textit{MFace\_ptr} mface, GEntity\_ptr gent):} Set the geometric model entity on which the face is classified.

@@

\item[]\textbf{\textit{void} MF\_Set\_ID(\textit{MFace\_ptr} mface,
\textit{int} id):} Explicitly set ID of a face and overwrite the ID
set by the \textbf{MF\_New} operator. Does not check for duplication of face
IDs.

@@

\item[]\textbf{\textit{void} MF\_Set\_Vertices(\textit{MFace\_ptr}
    mface, \textit{int} n, \textit{MVertex\_ptr} *verts):} Set the
  vertices of the face. The ordered set of vertices (ccw around the
  face) is passed in through an array along with the number of
  vertices. This routine will collect/build all lower order
  topological information (edges, edge directions in the face) as needed by the face.

\item[]\textbf{\textit{void} MF\_Replace\_Edge(\textit{MFace\_ptr}
    mface, \textit{MEdge\_ptr} edge, \textit{MEdge\_ptr} nuedge,
    \textit{int} dir):} \textit{THIS FUNCTION HAS BEEN SUPERSEDED BY
    \textbf{MF\_Replace\_Edges}}.

\item[]\textbf{\textit{void} MF\_Replace\_Edge\_i(\textit{MFace\_ptr}
    mface, \textit{int} i, \textit{MEdge\_ptr} nuedge, \textit{int}
    dir):} \textit{THIS FUNCTION HAS BEEN SUPERSEDED BY
    \textbf{MF\_Replace\_Edges\_i}}.

\item[]\textbf{\textit{void} MF\_Replace\_Edges(\textit{MFace\_ptr}
    mface, \textit{int} nold, \textit{MEdge\_ptr} *oldedges,
    \textit{int} nnu, \textit{MEdge\_ptr} *nuedges):} Replace a set of
  edges in the face with another set of edges. The direction in which
  the new edges are to be used in the face are automatically deduced.
  This function is relevant only for full representations in MSTK.

\item[]\textbf{\textit{void} MF\_Replace\_Edges\_i(\textit{MFace\_ptr}
    mface, \textit{int} nold, \textit{int} i, \textit{int} nnu,
    \textit{MEdge\_ptr} *nuedges):} Replace the \textit{nold} edges in
  the face starting with the i'th edge and going ccw around the face
  with a new set of edges. The directions in which the new edges are
  used in the face are automatically deduced. This function is
  relevant only for full representations in MSTK.

@@

@@

\item[]\textbf{\textit{void} MF\_Insert\_Vertex(\textit{MFace\_ptr} mface,
\textit{MVertex\_ptr} nuvertex, \textit{MVertex\_ptr} b4vertex):}
Insert a vertex in the face before \textbf{b4vertex} w.r.t. a ccw
ordering of the vertex faces.

\item[]\textbf{\textit{void} MF\_Replace\_Vertex\_i(\textit{MFace\_ptr}
mface, \textit{MVertex\_ptr} nuvertex, \textit{int} i):} Insert a new
vertex before vertex i in the face w.r.t. a ccw ordering of vertices.

\item[]

@@

\item[]

\item[]\textbf{\textit{MFace\_ptr} MVs\_CommonFace(\textit{int} nv,
    \textit{MVertex\_ptr} *fverts):} Return a face connected to all
  the given mesh vertices. Returns NULL if no such face exists.

\item[]\textbf{\textit{MFace\_ptr} MEs\_CommonFace(\textit{int} ne,
    \textit{MEdge\_ptr} *fedges):} Return a face connected to all
  the given mesh edges. Returns NULL if no such face exists.

\item[]

@@

\item[]\textbf{\textit{void} MR\_Delete(\textit{MRegion\_ptr} mregion,
    \textit{int} keep):} Delete the region. Deletes all topological
  information embedded in the region. If \textbf{keep} is 0, the
  region is removed from the mesh and all topological and geometric
  information embedded in the region is destroyed. If \textbf{keep} is
  1, the region is marked as type \textit{MDELREGION} and removed from
  the mesh but the region is not destroyed. Also, the vertices, edges
  and faces of this region no longer point up to this region.

\item[]\textbf{\textit{void} MR\_Restore(\textit{MRegion\_ptr}
    mregion):} Restore a temporarily deleted region. The region type
  is restored from \textit{MDELREGION} to \textit{MREGION} and the
  region is added back to the mesh. The vertices, edges and faces of
  the region once again point back to the region.

\item[]

\item[]\textbf{\textit{void} MR\_Set\_GEntity(\textit{MRegion\_ptr}
    mregion, GEntity\_ptr gent):} Set the geometric model entity on
  which the region is classified.

\item[]\textbf{\textit{void} MR\_Set\_GEntDim(\textit{MRegion\_ptr}
    mregion, \textit{int} gdim):} Set the dimension of the geometric
  model entity on which the region is classified.

\item[]\textbf{\textit{void} MR\_Set\_GEntID(\textit{MRegion\_ptr}
    mregion, \textit{int} gid):} Set the ID of the geometric model
  entity on which the region is classified.

\item[]\textbf{\textit{void} MR\_Set\_ID(\textit{MRegion\_ptr}
    mregion, \textit{int} id):} Explicitly set ID of a region and
  overwrite the ID set by the \textbf{MR\_New} function. Does not
  check for duplication of region IDs.

@@

\item[]\textbf{\textit{void} MR\_Set\_Vertices(\textit{MRegion\_ptr}
    mregion, \textit{int} nv, \textit{MVertex\_ptr} *mvertices):} Set
  the vertices of the region. This routine will collect/build all
  lower order topological information (edges, edge directions in the
  face) as needed by the face. For standard elements, the vertices
  must be ordered as indicated in Appendix~\ref{app:reg_conventions},
  while \textbf{nf} can be 0 and \textbf{rfv\_template} can be NULL.
  For non-standard elements, \textbf{nf} is the number of faces of the
  polyhedron and \textbf{rfv\_template} gives the vertices used in each
  face. More precisely, \textbf{rfv\_template} has \textbf{nfv}
  pointers to integer array $i$. The first entry of each
  \textbf{rfv\_template$[i]$} represents the number of vertices in that
  face and the remaining entries represent the list of vertices of the
  face listed so that the face defined by them points outward.

\item[]\textbf{\textit{void} MR\_Replace\_Face(\textit{MRegion\_ptr}
    mregion, \textit{MFace\_ptr} mface, \textit{MFace\_ptr} nuface,
    \textit{int} dir):} Replace a face of the region with another
  face. The direction in which the new face is used in the region must
  also be supplied. This function is only relevant for full
  representations in MSTK.

@@

\item[]\textbf{\textit{int} MEnt\_OrigDim(\textit{MEntity\_ptr} mentity):}
Returns the original topological dimension or type of generic entity before it
was temporarily deleted.

@@

\item[]\textbf{\textit{GEntity\_ptr}
    MEnt\_GEntity(\textit{MEntity\_ptr} mentity):} Returns a pointer
  or handle to geometric model entity that the entity is classified
  on.

\item[]

\item[]\textbf{\textit{void} MEnt\_Set\_AttVal(\textit{MEntity\_ptr}
    ent, \textit{MAttrib\_ptr} attrib, \textit{int} ival,
    \textit{double} lval, \textit{void} *pval):} Set the value of an
  attribute for given mesh entity. Depending on whether the attribute
  is integer, double or pointer, the appropriate entry in the argument
  list is specified.

\item[]\textbf{\textit{void} MEnt\_Rem\_AttVal(\textit{MEntity\_ptr}
    ent, \textit{MAttrib\_ptr mattrib}:} Clear the value of the given
  attribute from the entity.

\item[]\textbf{\textit{int} MEnt\_Get\_AttVal(\textit{MEntity\_ptr}
    ent, \textit{MAttrib\_ptr} int *ival, double *rval, double
    **pval):} Get the value of an attribute from an entity.  Depending
  on the attribute type, either \textbf{ival}, \textbf{rval} or
  \textbf{pval} is returned.

\newpage
\subsection{Mesh Attributes}

\item[]\textbf{\textit{MAttrib\_ptr} MAttrib\_New(\textit{Mesh\_ptr}
    mesh, \textit{const char} *att\_name, \textit{MAttType} att\_type,
    \textit{MType} entdim):} Define a new mesh attribute. Along with
  the mesh to which this attribute is assigned (\textbf{mesh}) and the
  name of the attribute (\textbf{att\_name}), the type of the
  attribute (\textbf{att\_type}) must be specified as \textbf{INT},
  \textbf{DOUBLE} or \textbf{POINTER}. Also, the dimension of the entity
    for which the attribute value can be set must be specified as
    \textbf{MVERTEX}, \textbf{MEDGE}, \textbf{MFACE}, \textbf{MREGION}
    or \textbf{MALLTYPE}.

\item[]\textbf{\textit{char} *MAttrib\_Get\_Name(\textit{MAttrib\_ptr}
    attrib, \textit{char} *att\_name):} Get the name of the given attribute.

\item[]\textbf{\textit{MAttType}
    MAttrib\_Get\_Type(\textit{MAttrib\_ptr} attrib):} Get the type of
  the attribute (Can return \textbf{INT}, \textbf{DOUBLE},
  \textbf{PVAL}).

\item[]\textbf{\textit{MType}
    MAttrib\_Get\_EntDim(\textit{MAttrib\_ptr} attrib):} Get the
  dimension (or type) of entity attribute can be asssigned to. Can be
  \textbf{MVERTEX}, \textbf{MEDGE}, \textbf{MFACE}, \textbf{MREGION}
  or \textbf{MALLTYPE}.

\item[]\textbf{\textit{void} MAttrib\_Delete(\textit{MAttrib\_ptr}
    attrib):} Delete an attribute.
